Manuscript progress report

### 2023-12-01 Docs/ProgressReportAppl.Rmd
data application

---
title: "Progress Report on NHANES Data"
author: "Ying Jin"
date: "2023-10-03"
output: 
  html_document:
    self_contained: no
    number_sections: true
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
    font: 12pt
---

@@

set.seed(516)

>>>>

---
title: "Progress Report on NHANES Data"
author: "Ying Jin"
date: "2023-10-03"
output: 
  html_document:
    self_contained: no
    number_sections: true
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
    font: 12pt
    keep_tex: true
---

@@

set.seed(121)

### 2023-12-01 Docs/manuscript.Rmd
data application

<!-- # NHANES data application -->

>>>>

# NHANES data application

We take 80% (7010) subjects for training, 20% (1753) for out-of-sample prediction.

In the GLMMadaptive model, I could only fit a model with random intercept. It took more than 20 minutes for model fitting.

```{r load_nhanes}
df_nhanes <- read_rds(here("Data/nhanes_bi.rds"))
load(here("Data/ApplOutput.RData"))
```

```{r nhance example}
df_nhanes %>% select(SEQN, Z, sind) %>% 
  mutate(Z = factor(Z, levels = 0:1, labels = c("Inactive", "Active"))) %>%
  mutate(SEQN = factor(SEQN, labels = 1:8763)) %>%
  ggplot()+
  geom_tile(aes(x=sind, y = SEQN, fill = Z))+
  labs(x="Time", y="Subject", title = "Overview of NHANES binary activity indicator")+
  theme(axis.text.y = element_blank())

```{r auc_fGFPCA_nhanes}
window3 <- seq(0, 1440, by = 240)

auc_mat_nhanes <- nhanes_pred_fgfpca %>%
  mutate(window = cut(sind, breaks = window3, include.lowest = T)) %>% 
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred240),
            auc2 = get_auc(Y, pred480),
            auc3 = get_auc(Y, pred720),
            auc4 = get_auc(Y, pred960),
            auc5 = get_auc(Y, pred1200)) %>%
  filter(window != "[0,240]") %>% 
  select(starts_with("auc"))

colnames(auc_mat_nhanes) <- c("4am", "8am", "12pm", "4pm", "8pm")
```

```{r auc_GLMMadaptive_nhanes}
auc_mat_nhanes2 <- nhanes_pred_adglmm %>%
  mutate(sind=t*1440) %>%
  mutate(window = cut(sind, breaks = window3, include.lowest = T)) %>% 
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred240),
            auc2 = get_auc(Y, pred480),
            auc3 = get_auc(Y, pred720),
            auc4 = get_auc(Y, pred960),
            auc5 = get_auc(Y, pred1200)) %>%
  filter(window != "[0,240]") %>% 
  select(starts_with("auc"))

colnames(auc_mat_nhanes2) <- c("4am", "8am", "12pm", "4pm", "8pm")
```

```{r}
data.frame(Window = c("4am-8am", "8am-12pm", "12pm-4pm", "4pm-8pm",
                      "8pm-12am"),
           auc_mat_nhanes, auc_mat_nhanes2, check.names = F) %>%
  kable(digits = 3, table.attr = "style = \"color: black;\"", caption = "Area Under the ROC curve") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "fGFPCA" = 5, "GLMMadaptive" = 5)) %>%
  add_header_above(c(" "= 1, "Maximum observation time" = 10))
```
